This is an example of article title

### 2019-06-22 paper/paper.tex
simd info

The interest in sorting and the great relevance of cache memory and parallelism to modern computing have naturally led to research on sorting algorithms that account for these factors. Processors offering SIMD (single instruction, multiple data) instructions and other forms of instruction-level parallelism started to become widely available in the early 2000s. One example is the introduction of SSE instructions in the x86 architecture~\cite[Chapter 1]{kusswurm18}. The current availability of processors with 512 bit registers underscores the necessity of being able to write software that utilizes vector operations, what can also benefit GPU programming.

>>>>

One particular form of parallelism that concerns the present work are SIMD (single instruction, multiple data) instructions~\cite{SIMDtut}. This is a form of computation where a same operation is applied to different independent memory elements simultaneously. These operations can be described as operating over {\em vectors}, where each {\em lane} contains the same data that would be involved in carrying out the same operations as a scalar version of the same program. SIMD parallelism is only suitable to specific problems, and its use may imply in memory access constraints and even clock speed reductions. There are still cases where it can bring great performance while being conveniently employed.

The interest in sorting and the great relevance of cache memory and parallelism to modern computing have naturally led to research on sorting algorithms that account for these factors. Processors offering SIMD instructions and other forms of instruction-level parallelism started to become widely available in the early 2000s. One example is the introduction of SSE instructions in the x86 architecture~\cite[Chapter 1]{kusswurm18}. The current availability of processors with 512 bit registers underscores the necessity of being able to write software that utilizes vector operations, what can also benefit GPU programming.
